### 2016-08-13 Theorem1_FP.tex
further cleaning up of Theorem 1

$\game{1}(A)$ and $\game{2}(A)$ attack 2 different filters. In $\game{1}(A)$, $F_{K_1}$ is replaced by a random function, whereas in $\game{2}(A)$, both $F_{K_0}$ and $F_{K_1}$ are replaced by random functions as shown below. Here, $\rho_1$ and $\rho_2$ are random functions sampled from $\Func{\univ,[m]}$.
\begin{align*}
\game{1}(A)\, : \, h_j(x) &= ( F_{K_0}(x) + j\cdot \rho_2(x)) \bmod m\\
\game{2}(A)\, : \, h_j(x) &= ( \rho_1(x) + j \cdot \rho_2(x)) \bmod m
\end{align*}
In $\game{3}(A)$, we replace the hash functions of $\HashOracle$ (in $\game{2}(A)$) with lazy sampling of elements from $[m]$. This brings us close to the classic Bloom filter's soundness condition, as now the hash indices sampled during a query are random points in $[m]$, and are independent of the hash indices used by the $\Rep$. As mentioned in \acnote{ref :{sec:intro}}, the soundness condition of a classic bloom filter is given as  $\Prob{h_1,h_2,\ldots,h_k \getsr \mathrm{Func}(\univ,[m])\colon M[h_1(y)]=1 \wedge \cdots \wedge M[h_k(y)]=1} \leq \epsilon$. Also, the $\QryOracle$ now sets $\bad$ to $\true$ if the queries indexed by the set $\mathcal{I}$ fail to be false-positives, or if any of the remaining queries are false-positives. It can be observed that the $\bad$ flag has no impact on the output of the $\QryOracle$, nor does it affect  the value returned by~$\game{3}$. Rather it lays foundation for $\game{4}(A)$. From these observations, 
\begin{align}
\Prob{\game{3}(A)=1 \wedge \neg\bad} &= \Prob{\game{3}(A)=1} \Prob{\game{3}(A) : \neg\bad}\label{eq:1} \\
\Prob{\game{2}(A)=1} &= \Prob{\game{3}(A)=1}\label{eq:2}
\end{align}
$\game{4}(A)$ is identical to $\game{3}(A)$ except it returns 0 if $\bad$ is set to true. So, by construction $\game{4}(A)$ and $\game{3}(A)$ are identical-untill-$\bad$. In addition, $\game{4}(A)$ returning 1 implies that bad is never set to true. Therefore,
\begin{equation}
\Prob{\game{4}(A)=1} = \Prob{\game{3}(A)=1 \wedge \neg\bad}\label{eq:3}
\end{equation}
From \Cref{eq:1,eq:2,eq:3}
\begin{equation}
\Prob{\game{4}(A)=1} =  \Prob{\game{2}(A)=1} \Prob{\game{3}(A) : \neg\bad} \label{eq:4}
\end{equation}
Since, probability of any set of $r$ queries indexed by set $\calI$ to be not false positives are equally likely to any other set sampled from $[\{1,2,\ldots,q\}]^r$, we have
\begin{equation}
\Prob{\game{3}(A) : \neg\bad} = \frac{1}{\dbinom{q}{r}}\label{eq:555}
\end{equation}
From \Cref{eq:4,eq:555}
\begin{equation}
\Prob{\game{4}(A)=1} = \Prob{\game{2}(A)=1}\frac{1}{\dbinom{q}{r}}\label{eq:6}
\end{equation}
In $\game{4}(A)$, $A$ wins $\ExpFPSecHash{B_{\mathrm{lin}},r}{A}$ after finding $r$ false positives indexed by $\calI$. Therefore, without loss of generality, it can be assumed that $A$ halts just after it finds the $r$ false positives, and outputs $\calZ$(of size $r$). Further, we can also assume that every point in $\calZ$ has already been queried to $\QryOracle$. This assumption can be  easily enforced (in the original security definitions) by counting as part of the number of queries~$q$, the points in $\mathcal{Z}$. Hence, if $\game{4}(A)=1$, there is a non-adaptive adversary~$D$ that finds~$r$ false positives against $\tilde{B}_{\mathrm{lin}}$, which is $B_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively as shown in \Cref{fig:D}. So,
\begin{align}
\nonumber \Prob{\ExpFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D} = 1} &= \Prob{\game{4}(A) = 1}\\
\mathrm{or} \nudge \AdvFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D} &= \Prob{\game{4}(A) = 1}\label{eq:7}
\end{align}
Let $\calF$ be the event of getting a false positive in a classic Bloom filter. Since, $D$ is a non-adaptive adversary, for $r=1$, it exactly simulates the classic Bloom filter game. Also, as the elements of $\calI$ are randomly sampled from $[\{1,2,\ldots,q\}]^r$, the event of any query indexed by $\calI$ being a false positive is mutually independent of any other query indexed by the same set. Hence,
\begin{align}
\nonumber \AdvFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D} &= [\Prob{\calF}]^r\\
&\leq \left( (1-e^{-kn/m})^k + O(1/n) \right)^r \label{eq:8}
\end{align}
Here, $\left( (1-e^{-kn/m})^k + O(1/n) \right)$ is the upper bound of $\calF$, as given by Kirsch et. al.\ref{KM}.
From \Cref{eq:7,eq:8},
\begin{equation}
\Prob{\game{4}(A)=1} \leq  \left( (1-e^{-kn/m})^k + O(1/n) \right)^r \label{eq:9}
\end{equation}
Using \Cref{eq:6} in \Cref{eq:9}
\begin{align}
\Prob{\game{2}(A)=1}\frac{1}{\dbinom{q}{r}} & \leq  \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\\
\Prob{\game{2}(A)=1} &\leq \dbinom{q}{r}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r\label{eq:10}
\end{align}
The PRF game of $F$ is shown in \Cref{fig:prf}. Let prf-adversaries $B_1, B_2$ be as shown in \Cref{fig:BGame1}.  By
construction, these simulate $\game{1}(A)$ and $\game{2}(A)$, respectively. When $b=0$, $B_1$ wins if $\game{1}(A)$ outputs 0; $B_2$ wins if $\game{2}(A)$ returns 0. When $b=1$, $B_1$ and $B_2$ exactly simulate $\game{0}(A)$ and $\game{1}(A)$. So, 
\begin{align}
\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=1} &= \Prob{\game{0}(A)=1}\label{eq:m1}\\
\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=1} &= \Prob{\game{1}(A)=1}\label{eq:m2}\\
\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=0} &= 1-\Prob{\game{1}(A)=1}\label{eq:m3}\\
\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=0} &= 1-\Prob{\game{2}(A)=1}\label{eq:m4}
\end{align}

%\caption{Game playing argument}\label{fig:Game}
\begin{figure}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{0}(A)}\\
$K_1, K_2 \getsr \calK$\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
$\calZ \getsr A^{\QryOracle}(\calS)$\\
if $|\calZ| < r$ or $\calZ \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists z \in \calZ$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
for $i = 1$ to $k$\\
\nudge $h_i(x) = F_{K_1}(x)+i \cdot F_{K_2}(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{1}(A)}\\
$K_1 \getsr \calK$\\
$\rho \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
$\calZ \getsr A^{\QryOracle}(\calS)$\\
if $|\calZ| < r$ or $\calZ \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists z \in \calZ$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
for $i=1$ to $k$\\
\nudge $h_i(x) = F_{K_1}(x)+i \cdot \rho(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{2}(A)}\\
$\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
$\calZ \getsr A^{\QryOracle}(\calS)$\\
if $|\calZ| < r$ or $\calZ \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists z \in \calZ$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
for $i=1$ to $k$\\
\nudge $h_i(x) = \rho_1(x)+i \cdot \rho_2(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{{$\game{3}(A)$},\fbox{$\game{4}(A)$}}\\
$c \gets 0$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
$\bad \gets \false$\\
%$\calY \gets \emptyset $\\
%$\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
$\calZ \getsr A^{\QryOracle}(\calS)$\\
if $|\calZ| < r$ or $\calZ \cap \calS \neq \emptyset$ then Ret 0\\
if $\forall z \in \calZ,\,\Qry^{\HashOracle}(M,z)=1$ then \\
\nudge if $\bad=\true$ then \fbox{Ret 0}\\
\nudge Ret 1\\
Ret 0\\\\
%if $|\calY| < t$ then \\ 
%\nudge Ret 0\\
%for $i=1$ to $t$ \\
%\nudge $z_i \getsr \calY $\\
%\nudge $\calY \gets \calY \setminus \{z_i\}$\\
%\nudge if $\Qry^{\HashOracle}(M,z_i)=0$ then\\
%\nudge \nudge Ret 0\\
%Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
%$\calY \gets \calY \cup \{x\}$\\
$c \gets c+1$\\
$v \gets \Qry^{\HashOracle}(M,x)$\\
if $c \in \mathcal{I}$ and $v\neq 1$ then\\
\nudge $\bad \gets \true$ \\
%\nudge \fbox{Ret 1} \\
if $c \not\in \mathcal{I}$ and $v\neq 0$ then\\
\nudge $\bad \gets \true$\\
%\nudge \fbox{Ret 0}\\
Ret~$v$\\\\
%
\oracle{$\HashOracle(x)$}\\
$a,b \getsr [m]$\\
for $i = 1$ to~$k$\\
\nudge $v_i = a+i \cdot b \bmod m$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{\Cref{thm1}:Game playing argument}\label{fig:Game}
\end{figure}

@@

%\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\begin{figure}
\centering
\fpage{0.9}{
\hpagessl{0.5}{0.5}
{
$\adversaryv{B_1^{\calO}}$\\
$K_1 \getsr \calK $\\
$\calS \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
When $A$ halts with output $\calZ'$: \\
\nudge if $|\calZ'| < r$ or $\calZ' \cap \calS \neq \emptyset$ then \\
\nudge \nudge Ret 0\\
\nudge if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge \nudge Ret 0\\
\nudge Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
$ \mathrm{Ret} \nudge F_{K_1}(x) + i\cdot \calO(x)$, for $i\in[1,k]$\\
}
{
$\adversaryv{B_2^{\calO}}$\\
%$d \getsr \bits $\\
%$\rho_2 \getsr Func(\univ, [m])$ \\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
When $A$ halts with output $\calZ'$: \\
\nudge if $|\calZ'| < r$ or $\calZ' \cap \calS \neq \emptyset$ then \\
\nudge \nudge Ret 0\\
\nudge if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge \nudge Ret 0\\
\nudge Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
%if $d=0$\\
$a \getsr [m]$\\
if $T[x] \neq \undefined$\\
\nudge $a \gets T[x]$\\
$T[x] \gets a$\\
$\mathrm{Ret} \nudge \calO(x) + i\cdot a$, for $i\in[1,k]$
}
}
\caption{\Cref{thm1}:Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\end{figure}

@@

%
\noindent
From \Cref{eq:m1,eq:m2,eq:m3,eq:m4},
\begin{align}
\nonumber \Prob{\ExpPRF{F}{B_1} = 1} &= .5\Prob{\ExpPRF{F}{B_1}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=1}\\
\nonumber 2\Prob{\ExpPRF{F}{B_1} = 1} &= 1-\Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
\nonumber (2\Prob{\ExpPRF{F}{B_1} = 1} - 1)  &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1}\\
 \AdvPRF{F}{B_1} &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \label{eq:11}\\
\nonumber& &\\
\nonumber \Prob{\ExpPRF{F}{B_2} = 1} &= .5\Prob{\ExpPRF{F}{B_2}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=1}\\
\nonumber 2\Prob{\ExpPRF{F}{B_2} = 1} &= 1-\Prob{\game{2}(A)=1} + \Prob{\game{1}(A)=1}\\
\nonumber (2\Prob{\ExpPRF{F}{B_2} = 1} - 1)  &= \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1}\\
 \AdvPRF{F}{B_2} &= \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1} \label{eq:12}
\end{align}

\noindent
Adding \Cref{eq:11,eq:12}, we have
\begin{equation}
\AdvPRF{F}{B_1} +\AdvPRF{F}{B_2} = \Prob{\game{0}(A)=1} - \Prob{\game{2}(A)=1}\label{eq:13}
\end{equation}

>>>>

 In $\game{1}(A)$, $F_{K_1}$ is replaced by a random function, whereas in $\game{2}(A)$, both $F_{K_0}$ and $F_{K_1}$ are replaced by random functions as shown below. Here, $\rho_1$ and $\rho_2$ are random functions sampled from $\Func{\univ,[m]}$.
%\begin{align*}
%\game{1}(A)\, : \, h_j(x) &= ( F_{K_0}(x) + j\cdot \rho_2(x)) \bmod m\\
%\game{2}(A)\, : \, h_j(x) &= ( \rho_1(x) + j \cdot \rho_2(x)) \bmod m
%\end{align*}

\begin{figure}
\centering
\fpage{0.9}{
\hpagessl{0.5}{0.5}
{
$\adversaryv{B_1^{\calO}}$\\
$K_1 \getsr \calK $\\
$\calS \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
When $A$ halts with output $\calZ'$: \\
\nudge if $|\calZ'| < r$ or $\calZ' \cap \calS \neq \emptyset$ then \\
\nudge \nudge Ret 0\\
\nudge if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge \nudge Ret 0\\
\nudge Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
$ \mathrm{Ret} \nudge F_{K_1}(x) + i\cdot \calO(x)$, for $i\in[1,k]$\\
}
{
$\adversaryv{B_2^{\calO}}$\\
%$d \getsr \bits $\\
%$\rho_2 \getsr Func(\univ, [m])$ \\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
When $A$ halts with output $\calZ'$: \\
\nudge if $|\calZ'| < r$ or $\calZ' \cap \calS \neq \emptyset$ then \\
\nudge \nudge Ret 0\\
\nudge if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge \nudge Ret 0\\
\nudge Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
%if $d=0$\\
$a \getsr [m]$\\
if $T[x] \neq \undefined$\\
\nudge $a \gets T[x]$\\
$T[x] \gets a$\\
$\mathrm{Ret} \nudge \calO(x) + i\cdot a$, for $i\in[1,k]$
}
}
\caption{\Cref{thm1}:Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\end{figure}

The PRF security notion is shown in \Cref{fig:prf}. Let
prf-adversaries $B_1, B_2$ be as shown in \Cref{fig:BGame1}.
Adversary~$B_1$ is constructed so that, if its challenge bit~$b=1$,
then it exactly simulates $\game{0}$ for~$A$; if $b=0$, it
simulates~$\game{1}$.  Similarly, adversary~$B_2$ simulates~$\game{1}$
if its challenge bit~$b=1$, and $\game{2}$ otherwise.  We can conclude
that 
\begin{align*}
\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=1} &= \Prob{\game{0}(A)=1} \\%\label{eq:m1}\\
\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=0} &= 1-\Prob{\game{1}(A)=1} \\%\label{eq:m3}\\
\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=1} &= \Prob{\game{1}(A)=1} \\%\label{eq:m2}\\
\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=0} &= 1-\Prob{\game{2}(A)=1} \\%\label{eq:m4}
\end{align*}
%
\noindent
By a standard conditioning of the PRF advantage, we have 
%From \Cref{eq:m1,eq:m2,eq:m3,eq:m4},
%\begin{align}
%\nonumber \Prob{\ExpPRF{F}{B_1} = 1} &= .5\Prob{\ExpPRF{F}{B_1}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=1}\\
%\nonumber 2\Prob{\ExpPRF{F}{B_1} = 1} &= 1-\Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
%\nonumber (2\Prob{\ExpPRF{F}{B_1} = 1} - 1)  &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1}\\
% \AdvPRF{F}{B_1} &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \label{eq:11}\\
%\nonumber& &\\
%\nonumber \Prob{\ExpPRF{F}{B_2} = 1} &= .5\Prob{\ExpPRF{F}{B_2}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=1}\\
%\nonumber 2\Prob{\ExpPRF{F}{B_2} = 1} &= 1-\Prob{\game{2}(A)=1} + \Prob{\game{1}(A)=1}\\
%\nonumber (2\Prob{\ExpPRF{F}{B_2} = 1} - 1)  &= \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1}\\
% \AdvPRF{F}{B_2} &= \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1} \label{eq:12}
%\end{align}
%\noindent
%Adding \Cref{eq:11,eq:12}, we have
\begin{equation*}
\Prob{\game{0}(A)=1} = \AdvPRF{F}{B_1} +\AdvPRF{F}{B_2} + \Prob{\game{2}(A)=1}%\label{eq:13}
\end{equation*}

In $\game{3}(A)$, we replace the random functions used in
$\HashOracle$ (in $\game{2}(A)$) with lazy sampling of elements from
$[m]$.  This change does not alter the behavior of the oracle, as the
random functions are (by the no-pointless-queries assumption on~$A$) always called on a new
value of~$x$.
%
Also, the $\QryOracle$ oracle now sets $\bad$ to $\true$ if the
queries indexed by the set $\mathcal{I}$ fail to be false-positives,
or if any of the remaining queries are false-positives. It can be
observed that the $\bad$ flag has no impact on the output of the
$\QryOracle$, nor does it affect  the value returned
by~$\game{3}$. Thus we have $\Prob{\game{2}(A)=1} =
\Prob{\game{3}(A)=1}$ and
\[
\Prob{\game{3}(A)=1 \wedge \game{3}(A): \neg\bad} = \Prob{\game{3}(A)=1} \Prob{\game{3}(A) : \neg\bad}%\label{eq:1} \\
\]

We note that $\game{3}$ and $\game{4}$ are
``identical-untill-$\bad$''~\cite{BeRo-gameplaying}.  In particular,
in $\game{4}$ returns 0 when $\game{3}$ would have returned 1 (i.e.,
the adversary outputs~$r$ false-positives) but $\bad=\true$.  
Moreover,  $\game{4}(A)$ returning 1 implies that $\bad$ is never set to $\true$. Therefore,
$\Prob{\game{4}(A)=1} = \Prob{\game{3}(A)=1 \wedge \neg\bad} =
\Prob{\game{3}(A)=1} \Prob{\game{3}(A) : \neg\bad}$, by our previous observation.

Before continuing the proof, a bit of intuition for the introduction
of the $\bad$-flag in games~$\game{3},\game{4}$.   Intuitively, if the index
set~$\mathcal{I}$ exactly predicts which of the $\QryOracle$ will be
false-positives (and, conversely, which will not be), then a
non-adaptive FP-finding adversary can ``guess'' which of~$A$'s queries require it
to return 1 when simulating the $\QryOracle$, and which require it to
return 0.  In this way, no queries ever actually need to be made.
Moving to a non-adaptive setting will allow us to connect to classical
results on the FP-rate of Bloom filters; more in a moment.

Now, consider $\Prob{\game{3}(A) : \neg\bad}$.  The indicated event
happens iff the $r$-set~$\calI$ contains exactly the indices of
$\QryOracle$-queries that are false-positives.  Since the value
of~$\bad$ does not alter the responses of~$\QryOracle$, the
set~$\mathcal{Z}$ output by~$A$ and the set~$\calI$ are independent.
Thus $\bad$ remains $\false$ after~$A$ halts with probability
$1/\dbinom{q}{r}$, and we have 
\begin{equation*}
\Prob{\game{3}(A)=1} = \frac{1}{\dbinom{q}{r}}\Prob{\game{4}(A)=1}
\end{equation*}

\fixme{Tom is here in rewriting the proof.}
Moving on $\game{4}(A)$, $A$ wins $\ExpFPSecHash{B_{\mathrm{lin}},r}{A}$ after finding $r$ false positives indexed by $\calI$. Therefore, without loss of generality, it can be assumed that $A$ halts just after it finds the $r$ false positives, and outputs $\calZ$(of size $r$). Further, we can also assume that every point in $\calZ$ has already been queried to $\QryOracle$. This assumption can be  easily enforced (in the original security definitions) by counting as part of the number of queries~$q$, the points in $\mathcal{Z}$. Hence, if $\game{4}(A)=1$, there is a non-adaptive adversary~$D$ that finds~$r$ false positives against $\tilde{B}_{\mathrm{lin}}$, which is $B_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively as shown in \Cref{fig:D}. So,
\begin{align}
\nonumber \Prob{\ExpFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D} = 1} &= \Prob{\game{4}(A) = 1}\\
\mathrm{or} \nudge \AdvFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D} &= \Prob{\game{4}(A) = 1}\label{eq:7}
\end{align}
Let $\calF$ be the event of getting a false positive in a classic Bloom filter. Since, $D$ is a non-adaptive adversary, for $r=1$, it exactly simulates the classic Bloom filter game. Also, as the elements of $\calI$ are randomly sampled from $[\{1,2,\ldots,q\}]^r$, the event of any query indexed by $\calI$ being a false positive is mutually independent of any other query indexed by the same set. Hence,
\begin{align}
\nonumber \AdvFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D} &= [\Prob{\calF}]^r\\
&\leq \left( (1-e^{-kn/m})^k + O(1/n) \right)^r \label{eq:8}
\end{align}
Here, $\left( (1-e^{-kn/m})^k + O(1/n) \right)$ is the upper bound of $\calF$, as given by Kirsch et. al.\ref{KM}.
From \Cref{eq:7,eq:8},
\begin{equation}
\Prob{\game{4}(A)=1} \leq  \left( (1-e^{-kn/m})^k + O(1/n) \right)^r \label{eq:9}
\end{equation}
Using \Cref{eq:6} in \Cref{eq:9}
\begin{align}
\Prob{\game{2}(A)=1}\frac{1}{\dbinom{q}{r}} & \leq  \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\\
\Prob{\game{2}(A)=1} &\leq \dbinom{q}{r}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r\label{eq:10}
\end{align}

%\caption{Game playing argument}\label{fig:Game}
\begin{figure}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{0}(A)}\\
$K_1, K_2 \getsr \calK$\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
$\calZ \getsr A^{\QryOracle}(\calS)$\\
if $|\calZ| < r$ or $\calZ \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists z \in \calZ$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
for $i = 1$ to $k$\\
\nudge $h_i(x) = F_{K_1}(x)+i \cdot F_{K_2}(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{1}(A)}\\
$K_1 \getsr \calK$\\
$\rho \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
$\calZ \getsr A^{\QryOracle}(\calS)$\\
if $|\calZ| < r$ or $\calZ \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists z \in \calZ$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
for $i=1$ to $k$\\
\nudge $h_i(x) = F_{K_1}(x)+i \cdot \rho(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
}
\fpage{.9}{
\hpagessl{.45}{.5}
{
\underline{\game{2}(A)}\\
$\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
$\calZ \getsr A^{\QryOracle}(\calS)$\\
if $|\calZ| < r$ or $\calZ \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists z \in \calZ$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
for $i=1$ to $k$\\
\nudge $h_i(x) = \rho_1(x)+i \cdot \rho_2(x) \bmod m$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{{$\game{3}(A)$},\fbox{$\game{4}(A)$}}\\
$c\gets 0$, $\bad\gets\false$\\
$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
$S \getsr \distr{\univ}{n}$\\
$M \getsr \Rep^{\HashOracle}(\calS)$\\
$\calZ \getsr A^{\QryOracle}(\calS)$\\
if $|\calZ| < r$ or $\calZ \cap \calS \neq \emptyset$ then Ret 0\\
if $\forall z \in \calZ,\,\Qry^{\HashOracle}(M,z)=1$ then \\
\nudge if $\bad=\true$ then \fbox{Ret 0}\\
\nudge Ret 1\\
Ret 0\\\\

\oracle{$\QryOracle(x)$}\\
$c \gets c+1$\\
$v \gets \Qry^{\HashOracle}(M,x)$\\
if $c \in \mathcal{I}$ and $v\neq 1$ then\\
\nudge $\bad \gets \true$ \\
if $c \not\in \mathcal{I}$ and $v\neq 0$ then\\
\nudge $\bad \gets \true$\\
Ret~$v$\\\\
%
\oracle{$\HashOracle(x)$}\\
$a,b \getsr [m]$\\
for $i = 1$ to~$k$\\
\nudge $v_i = a+i \cdot b \bmod m$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{\Cref{thm1}:Game playing argument}\label{fig:Game}
\end{figure}

@@

%\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}

@@
